GNSS displacement detection based on Bayesian inference

### 2020-11-14 paper/manuscript.tex
add introduction

\section{Introduction}
\label{intro}

\section{Methodology}
\subsection{Relative real-time kinematic (RTK)}
RTK is widely used in structural health monitoring, landslide monitoring, and other fields due to its high positioning accuracy and real-time efficiency. The observation model, the state model, and the extended Kalman filtering process of RTK are introduced below. 
\subsubsection{Observation model}
The double-difference (DD) observation equation of relative positioning among base receiver, rover receiver, and satellites $j$, $k$ is defined in (\ref{eq_dd_obs})\citep{teunissen2017springer}.
\begin{figure*}
	\begin{equation}
	\left. \begin{array}{l}
	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - \Delta \nabla \delta I_{\Phi {i_{br}}}^{jk} + \Delta \nabla \delta _{tro{p_{br}}}^{jk} + \Delta \nabla \delta M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla \delta I_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \delta _{tro{p_{br}}}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla \delta M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}
	\end{array} \right\}
	\label{eq_dd_obs}
	\end{equation}
\end{figure*}
In this observation equation, $\Delta \nabla $ denotes the DD operator, $i$ denotes the frequency; $b$ and $r$ denote base station and rover station respectively; $\Delta \nabla P_{{{i}_{br}}}^{jk}$ and $\Delta \nabla \Phi _{{{i}_{br}}}^{jk}$ denote pseudo-range and carrier-phase DD observations, respectively; $\Delta \nabla \rho _{br}^{jk}$ is the DD geometric distance between receivers and satellites; $\Delta \nabla \delta M_{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \delta M_{{{\Phi }_{{{i}_{br}}}}}^{jk}$ denote pseudo-range and carrier-phase multipath error, respectively; $\Delta \nabla \varepsilon _{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \varepsilon _{{{\Phi }_{{{i}_{br}}}}}^{jk}$ represent DD observation error of pseudo-range and carrier-phase, respectively; $\Delta \nabla \delta I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations; $\Delta \nabla \delta _{tro{{p}_{br}}}^{jk}$is the DD tropospheric delay between receivers and satellites. For the short baseline, the atmospheric error can be ignored, so the above DD observation equation is simplified as (\ref{eq_dd_obs_simplified}).
\begin{figure*}
	\begin{equation}
	\left. \begin{array}{l}
	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla \delta M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla \delta M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}\end{array} \right\}
	\label{eq_dd_obs_simplified}
	\end{equation}

Due to the complex spatiotemporal characteristics of observation errors, there are unmodeled error components in time series\citep{shen2020site}. To weaken the influence of these factors, the wavelet analysis tool is introduced as follows.

@@

\section{Experiments and Results}
To verify the feasibility of the proposed method, we carried out a series of experiments, including a simulation experiment and a field experiment. In the simulation experiment, data affected by noise and a trend item is simulated. In the field experiment, several displacement changes were triggered manually, and the relative real-time kinematic model is used to process the GNSS observations.
\subsection{Simulation experiment}

>>>>

\section{Introduction}
\label{intro}
%全球定位系统系统的应用-》位移探测
%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
%传统测量仪器的弊端，GNSS位移探测的优势。
In recent decades, GNSS has been widely used in navigation, surveying, and civil aviation as a positioning method. Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring, industrial measurement, and other fields. Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence.

%位移探测算法回顾，传统位移探测的弊端
%位移探测的短板
%本文拟采取的措施弥补这些短板
%Bayes的优势，并且调研一下前人是否尝试同样的方法干过这类事情
%引入本文的研究内容和贡献
%引入文章结构

\section{Methodology}
\label{method}

@@

\subsection{Relative real-time kinematic (RTK)}
RTK is widely used in structural health monitoring, landslide monitoring, and other fields due to its high positioning accuracy and real-time efficiency. The observation model, the state model, and the extended Kalman filtering process of RTK are introduced below. 
\subsubsection{Observation model}
The double-difference (DD) observation equation of relative positioning among base receiver, rover receiver, and satellites $j$, $k$ is defined in (\ref{eq_dd_obs})\citep{teunissen2017springer}.
\begin{figure*}
	\begin{equation}
	\left. \begin{array}{l}
	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - \Delta \nabla \delta I_{\Phi {i_{br}}}^{jk} + \Delta \nabla \delta _{tro{p_{br}}}^{jk} + \Delta \nabla \delta M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla \delta I_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \delta _{tro{p_{br}}}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla \delta M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}
	\end{array} \right\}
	\label{eq_dd_obs}
	\end{equation}
\end{figure*}
In this observation equation, $\Delta \nabla $ denotes the DD operator, $i$ denotes the frequency; $b$ and $r$ denote base station and rover station respectively; $\Delta \nabla P_{{{i}_{br}}}^{jk}$ and $\Delta \nabla \Phi _{{{i}_{br}}}^{jk}$ denote pseudo-range and carrier-phase DD observations, respectively; $\Delta \nabla \rho _{br}^{jk}$ is the DD geometric distance between receivers and satellites; $\Delta \nabla \delta M_{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \delta M_{{{\Phi }_{{{i}_{br}}}}}^{jk}$ denote pseudo-range and carrier-phase multipath error, respectively; $\Delta \nabla \varepsilon _{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \varepsilon _{{{\Phi }_{{{i}_{br}}}}}^{jk}$ represent DD observation error of pseudo-range and carrier-phase, respectively; $\Delta \nabla \delta I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations; $\Delta \nabla \delta _{tro{{p}_{br}}}^{jk}$is the DD tropospheric delay between receivers and satellites. For the short baseline, the atmospheric error can be ignored, so the above DD observation equation is simplified as (\ref{eq_dd_obs_simplified}).
\begin{figure*}
	\begin{equation}
	\left. \begin{array}{l}
	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla \delta M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla \delta M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}\end{array} \right\}
	\label{eq_dd_obs_simplified}
	\end{equation}

\section{Experiments and Results}
To verify the feasibility of the proposed method, we carried out a series of experiments, including simulation experiments and field experiments. In the simulation experiment, the data affected by different noises are simulated. In the field experiment, several displacement changes were triggered manually, and the relative real-time kinematic model is used to process the GNSS observations.
\subsection{Simulation experiment}
